% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Dylan Yin}

\basicInfo{
  \email{dylanyin@foxmail.com} \textperiodcentered\
  \phone{(+86) 156-9740-5976} \textperiodcentered\
  % \linkedin[billryan8]{https://www.linkedin.com/in/billryan8}
}
\section{\faHeart\  Self-evaluation}
\begin{onehalfspacing}
\begin{itemize}
\item Good at English reading, CET-6 get 509 points
\item Have a deeper understanding in python language, knowing how to write pythonic code
%\item 对编程非常感兴趣，业余学习 \texttt{Go} \texttt{Java} 等语言
\item Interested in increasing code efficiency, love Emacs and Vim
\item Love work in Linux, familiar with Git workflow
\end{itemize}
\end{onehalfspacing}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Huawei Technologies Co., Ltd. (Outsource Job)} Shenzhen}{Aug. 2021 -- Present}
\role{Python, Flask, Sqlite}{Python Developer}
\begin{onehalfspacing}
Image Packing Tool

Brief introduction: encrypt and sign the binary that compiled by C, padding the information according to the config file, finally generate the image that can burn to the chip.
\begin{itemize}
\item Used the \texttt{Flask} as the back-end web framework and the \texttt{Bootstrap5} as the front-end web framework
\item Implemented login feature, so that the client can login and manage their encryption key
\item Used the \texttt{Sqlite} database, and easy migrate to other database by using \texttt{Flask-Migrate}
\item Docked the KMS (key management system) and PKI (public key infrastructure)
\item Implemented file upload feature by using the \texttt{Flask-File-Upload}
\end{itemize}
\end{onehalfspacing}

\datedsubsection{\textbf{K\&D Technology Co., Ltd.} Shenzhen}{Jun. 2020 -- Aug. 2021}
\role{Python, SQL Server, PostgreSQL, Pandas, FineBI, FineReport}{Data Engineer}
\begin{onehalfspacing}
\textbf{User Profile}

Brief introduction: User profile is generated from multiple dimensions such as product yield rate, overtime hours, and leadership evaluation to provide reference for employee promotion and self-improvement.
\begin{itemize}
\item Writed SQL to query data from HRMS's database.
\item Used \texttt{Kettle Etl Tool} extract data into the data warehouse
\item Used \texttt{Pandas} to generate label data every day
\item Designed kanban using FineBI, leader can check employees' profile on their own
\end{itemize}
\end{onehalfspacing}

\begin{onehalfspacing}
\textbf{Specification Digitalization}

Brief introduction: Extract data from the specifications in the history, store the data into the data warehouse, using FineBI build the kanban so that salesman can quickly check if a product had been produced before.
\begin{itemize}
\item Used \texttt{Python-docx} and \texttt{Pdfplumber} perform data extract
\item Used \texttt{Pandas} to clean the data
\item Used \texttt{Kettle} store the cleaned data into the data warehouse
\item Used FineBI design the kanban,
\item Integrated FineBI into Wechat Work, open access permission to the salesman
\end{itemize}
\end{onehalfspacing}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Hunan Institute of Science and Technology}, Hunan}{2016 -- 2020}
\textit{B.Eng.} in Electrical Engineering and Automation
% \section{Project in University}
\\~\\
\textbf{Computer Vision and Deep Learning}

\begin{onehalfspacing}
Hyperspectral Image Classification
\begin{itemize}
  \item Used \texttt{Sklearn} to perform PCA method to get dimensions reduced
  \item Used \texttt{Pandas} processing the data
  \item Builded the neural network using \texttt{Pytorch}
  \item Classify the Hyperspectral Image use trained neural network
\end{itemize}
\end{onehalfspacing}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

% \section{\faCogs\ Skills}
% \begin{itemize}[parsep=0.5ex]
%   \item Programming Languages: C == Python > C++ > Java
%   \item Platform: Linux
%   \item Development: Web, xxx
% \end{itemize}

% \section{\faHeartO\ Honors and Awards}
% \datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
% \datedline{Other awards}{2015}

% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/username
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
